Quality Definitions of Qualities

### 2020-01-19 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
added testability

\subsection{{Correctness} \oo{owner}}

\begin{defn} \label{Correctness_Selected}
  A program is functionally correct if it behaves according to its stated
  functional specifications \citep{GhezziEtAl2003}.  \wss{Is this verbatim from
    the original source?  If not, we should show those parts that are verbatim
    in quotes, so that readers know the parts that were developed by us.}
  \oo{Yes, verbatim}

\end{defn}

\begin{defn}
  The degree to which a system is free from defects in its specification, design, and implementation, is its correctness \citep{wilson2009quality}.  \oo{Need to verify this definition, still searching for this paper}
\end{defn}

@@

\begin{defn} 
  The extent to which a program satisfies its specifications and fulfills the
  user's mission objectives \citep{McCallEtAl1977}. \oo{definition is checked with pdf} \wss{Great!  Did you add the Mccall paper to the pub repo?}
\oo{I will}
\end{defn}

@@

\begin{defn}
  Correctness from software engineering perspective can be defined as the
  adherence to the specifications that determine how users can interact with the
  software and how the software should behave when it is used correctly
  \citep{Tutorialspoint}.
\end{defn}

@@

Definition~\ref{Correctness_Selected} rephrased: A program is functionally correct if it behaves according to its stated specifications  \oo{Proposed definition updated to Ghezzi's}

@@

@@

>>>>

\subsection{\notdone{Correctness} \oo{owner}}

\begin{defn} \label{Correctness_Selected}
  A program is functionally correct if it behaves according to its stated
  functional specifications \citep{GhezziEtAl2003}.  
\end{defn}

@@

\begin{defn} 
  The extent to which a program satisfies its specifications and fulfills the
  user's mission objectives \citep{McCallEtAl1977}. \oo{paper added to repo} 
\end{defn}

@@

@@

Definition~\ref{Correctness_Selected} rephrased: A program is correct if it behaves according to its stated specifications

@@

	The degree to which a system is free from defects in its specification, design, and implementation, is its correctness \citep{wilson2009quality}.  \oo{this book is unavailable to verify this definition}

@@

\subsection{\notdone{Testability} \oo{owner}}
\begin{defn}
	Code possesses the characteristic testability to the extent that it facilitates the establishment
	of verification criteria and supports evaluation of its performance \citep{boehm1976quantitative}.
\end{defn}
